Similar Sentence Detection Using Locality Sensitive Hashing Technique on Wikipedia

### 2013-11-02 article/article-draft.tex
Added unique title count back in to histogram code

All of our experiments were run against an XML dump of current English-language Wikipedia (enwiki) articles (as of 4/2013) obtained from dumps.wikimedia.org. The enwiki dump is approximately 40G in size and contains 4,113,785 articles (after excluding certain non-article page types). Running the first four steps of our application (up to but not including the final edit distance filtering pass) against the enwiki dump on a shared cluster of 16 nodes with (15 GB RAM and 4 cores each) took $\approx 2$ hours.

After minhashing and deduplification, we found a total of 9,465,881 similar article/sentence pairs. After clustering these pairs, the total number of similar sentence clusters was 415,936, including 1,792,748 unique article/sentence pairs over 759,297 article titles. The total number of unique sentences over all cluster was 1,305,359.

>>>>

All of our experiments were run against an XML dump of current English-language Wikipedia (enwiki) articles (as of 7/2013) obtained from dumps.wikimedia.org. The enwiki dump is approximately 42G in size and contains 10,218,778 articles (after excluding certain non-article page types). Running our application on the enwiki dump on a shared cluster of 16 nodes (20 GB RAM and 4? cores each) took $\approx$ 25 minutes.

The total number of similar sentence clusters was 1,151,640, including 3,496,074 article/sentence pairs over  article titles. The total number of unique sentences over all cluster was 1,305,359.
